Certified Knowledge Compilation \\ with Application to Verified Model Counting \\ Experimental Details

### 2023-08-27 doc/JAIR/jair-data.tex
Summary statistics

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 0.70]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log,
      legend style={at={(0.30,0.96)}},
      legend cell align={left},
                              x post scale=1.8, y post scale=2.4,
                              xmode=log,
                              xmin=0.01,xmax=4000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ymin=0.01, ymax=29000,
                              ytick={0.01, 0.1,1.0,10,100,1000,10000,100000}, yticklabels={0.01, 0.1, 1.0, 10, 100, {1,000},{10,000},{100,000}},
                              xlabel={D4 runtime (seconds)}, ylabel={CPOG generation and checking runtime (seconds)},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/seconds-summary}
    \input{data-formatted/seconds-summary-structured-only}
    \input{data-formatted/seconds-summary-onesided}
    \input{data-formatted/seconds-summary-failures}
    \legend{
      \scriptsize \textsf{Full validation, Hybrid},
      \scriptsize \textsf{Full validation, Structural},
      \scriptsize \textsf{One-sided validation},
      \scriptsize \textsf{Resource limit exceeded},
    }
    \addplot[mark=none, dashed] coordinates{(0.01,25000) (4000, 25000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,20000) (4000,20000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.1,0.01) (10000.0,1000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.01) (10000.0,10000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.1) (2000,20000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (200, 20000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,10.0) (20, 20000)};
    \node[left] at (axis cs: 0.9,0.12) {$0{.}1\times$};
    \node[left] at (axis cs: 0.09,0.12) {$1\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};
    \node[left] at (axis cs: 0.09,120.0) {$1000\times$};
       \end{axis}

@@

@@

>>>>

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 0.70]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log,
      legend style={at={(0.30,0.96)}},
      legend cell align={left},
                              x post scale=1.8, y post scale=2.4,
                              xmode=log,
                              xmin=0.01,xmax=4000,
                              xtick={0.01, 0.1,1.0,10,100,1000,10000}, xticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}, {10,000}},
                              ymin=0.01, ymax=29000,
                              ytick={0.01, 0.1,1.0,10,100,1000,10000,100000}, yticklabels={0.01, 0.1, 1.0, 10, 100, {1,000},{10,000},{100,000}},
                              xlabel={D4 runtime (seconds)}, ylabel={CPOG generation and checking runtime (seconds)},
%                              title={D4 Defining Clause Generation}
            ]
    \input{data-formatted/seconds-summary}
    \input{data-formatted/seconds-summary-structured-only}
    \input{data-formatted/seconds-summary-onesided}
    \input{data-formatted/seconds-summary-failures}
    \legend{
      \scriptsize \textsf{Full validation, Hybrid},
      \scriptsize \textsf{Full validation, Structural},
      \scriptsize \textsf{One-sided validation},
      \scriptsize \textsf{Resource limit exceeded},
    }
    \addplot[mark=none, dashed] coordinates{(0.01,25000) (4000, 25000)};) 
    \addplot[mark=none, color=lightblue] coordinates{(0.01,20000) (4000,20000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.1,0.01) (10000.0,1000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.01) (10000.0,10000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.1) (2000,20000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (200, 20000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,10.0) (20, 20000)};
    \node[left] at (axis cs: 0.9,0.12) {$0{.}1\times$};
    \node[left] at (axis cs: 0.09,0.12) {$1\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};
    \node[left] at (axis cs: 0.09,120.0) {$1000\times$};
       \end{axis}

@@

Figure~\ref{fig:d4:cpog} compares the running time for the combination
of generating and checking the CPOG file (Y axis), versus the running
time for C4 (X Axis).  If we compare the ratio between the two we find the following:
\begin{itemize}
\item Min = 0.27 (i.e., Verification chain was $3.64\times$ faster
\item Max = 177.0
\item Median = 12.5
\end{itemize}

@@

Figure~\ref{fig:defining:total} compares the total number of clauses in the CPOG representation (Y axis) versus the number of defining clauses (X axis).  Since the former include the latter, the ratio between these cannot be less than 1.0.
Comparing the ratios gives:
\begin{itemize}
\item Min = 1.02
\item Max = 9460.2
\item Median = 2.29
\end{itemize}
